---
title: "About R Functions"
output: html_notebook
---

Functions are a great way to package scripts that you use frequently; it makes them easy to reuse and also let's you tinker with your script in a single place and have the changes available wherever you call the function. Using custom functions might mean turning away from a script-based workflow. If a script is a few lines of dialogue from a tv show, the function is the whole episode or at least a scene with a beginning, middle, and end. If you find yourself cutting and pasting lines from a script and using them elsewhere, it might be time to give functions a look.

Functions run the scripts stored inside of them when they are called, and return only a single object at the end, so your environment doesn't get cluttered with all of your intermediate steps toward your goal.

The function is an object like any other in R. You've already been using them all the time, but you may not have thought about them as objects because, unless you define them, they are normally hidden from view. To look at the function object, simply call its name, and the function definition will be printed. Maybe you've seen this happen sometimes when you forgot to write the parantheses.

```{r}
#I called the function!
Sys.time()
```

```{r}
#I only inspected the function
Sys.time
```


To actually execute or call the function, use parantheses after the name. But you already knew that. The great thing about functions is that they are really easy to write yourself! To make a function in R, use the `function()` function :)

```{r hello-world}
hw<-function() 'Hello world!'
hw()
hw
```

All our `hw` function did was return the last (and only) object defined inside of it. A great feature of functions is that you can supply arguments, and even give them sensible defaults.
```{r}
hw<-function(saywhat='world') {
	paste0('Hello ',saywhat,'!')
}
hw()

```

```{r}
hw('peanut butter')
```
And again calling the name of the function without parantheses prints the contents of the function without executing it.
```{r}
hw
```
